### 2021-01-22 ch05_paper_ecs/paper_ecs.tex
Added figures for chapter 05

>>>>

\begin{figure}[p]
  \centering
  \begin{subfigure}[b]{\SubfigureWidth{}}
    \includegraphics[width=\columnwidth]{
      ch05_paper_ecs/figs/scatterplot_merged_training_data_BRI.pdf}
    \caption{}
    \label{fig:05:bri_cox_lip:a}
  \end{subfigure}
  ~
  \begin{subfigure}[b]{\SubfigureWidth{}}
    \includegraphics[width=\columnwidth]{
      ch05_paper_ecs/figs/target_distribution_training_data_BRI.pdf}
    \caption{}
    \label{fig:05:bri_cox_lip:b}
  \end{subfigure}
  \\
  \begin{subfigure}[b]{\SubfigureWidth{}}
    \includegraphics[width=\columnwidth]{
      ch05_paper_ecs/figs/scatterplot_merged_training_data_COX.pdf}
    \caption{}
    \label{fig:05:bri_cox_lip:c}
  \end{subfigure}
  ~
  \begin{subfigure}[b]{\SubfigureWidth{}}
    \includegraphics[width=\columnwidth]{
  ch05_paper_ecs/figs/target_distribution_training_data_COX.pdf}
    \caption{}
    \label{fig:05:bri_cox_lip:d}
  \end{subfigure}
  \\
  \begin{subfigure}[b]{\SubfigureWidth{}}
    \includegraphics[width=\columnwidth]{
      ch05_paper_ecs/figs/scatterplot_merged_training_data_LIP.pdf}
    \caption{}
    \label{fig:05:bri_cox_lip:e}
  \end{subfigure}
  ~
  \begin{subfigure}[b]{\SubfigureWidth{}}
    \includegraphics[width=\columnwidth]{
  ch05_paper_ecs/figs/target_distribution_training_data_LIP.pdf}
    \caption{}
    \label{fig:05:bri_cox_lip:f}
  \end{subfigure}
  \caption{xD. Updated from
    \textcite{Schlund2020a}.}
  \label{fig:05:bri_cox_lip}
\end{figure}
